Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v) \in \J(R_1, ..., R_{k-3}, H', V)$. Note that $\bm{t}[k-2] = h'$ must intersect with $v$ as $\bm{t}$ is a result tuple of the $(k-1)$-SJ. If $p$ is the intersection point between $h$ and $v$, we define the {\em effective horizontal segment} of $\bm{t}$ as the horizontal segment from the left endpoint of $h'$ to $p$.
\myeqn{
    \contained_{R_{k-2}}(\bm{t}) &=& \{r_{k-2} \in R_{k-2} \mid \text{ the effective horizontal } \nn \\
    && \text{segment of $\bm{t}$ is contained in $r_{k-2}$}   \}
    \nn
}
The above definition should not be confused with \eqref{eqn:contained}, where the $\contained$ function takes a horizontal segment as the input.

@@

>>>>

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v) \in \J(R_1, ..., R_{k-3}, H', V)$. Note that $\bm{t}[k-2] = h'$ must intersect with $v$ as $\bm{t}$ is a result tuple of the $(k-1)$-SJ. If $p$ is the intersection point between $h$ and $v$, we define the {\em effective horizontal segment} of $\bm{t}$ as the horizontal segment from the left endpoint of $h'$ to $p$.
\myeqn{
    \contained_{R_{k-2}}(\bm{t}) &=& \{r_{k-2} \in R_{k-2} \mid \text{ the effective horizontal } \nn \\
    && \text{segment of $\bm{t}$ is contained in $r_{k-2}$}   \}
    \label{eqn:type2:contained-t}
}
The above definition should not be confused with \eqref{eqn:contained}, where the $\contained$ function takes a horizontal segment as the input.

@@

\extraspacing {\bf Computing the ``$\bm{\contained_{R_{k-2}}(t)}$'' Sets.} We are ready to produce $\contained_{R_{k-2}}(h^*)$, defined in \eqref{eqn:type2:contained-t}, for any $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$, based on Statement (2) of Lemma~\ref{lmm:hv:type2:contained-h*}. First, fetch the (already computed) minimal segment $h^*$ of $h'$ in $O(1)$ time. Then, scan the rectangles $r$ in $\contained_{R_{k-2}}(h^*)$ in descending order of $\xright(r)$. For each $r$ scanned, check whether $r \in 
\contained_{R_{k-2}}(\bm{t})$, or equivalently, whether $r$ covers the intersection point between $h$ and $v$; this takes $O(1)$ time. Abort the scan as soon as $r \notin 
\contained_{R_{k-2}}(\bm{t})$. This way, we compute $\contained_{R_{k-2}}(t)$ in $O(k + |\contained_{R_{k-2}}(t)|)$ time. Doing so for all $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$ takes $O(k \cdot |\J| + \sum_\bm{t} |\contained_{R_{k-2}}(t)|) = O(k \cdot \out)$ time, where the derivation used Lemma~\ref{lmm:hv:type2:recur-output} and statement (3) of Lemma~\ref{lmm:hv:type2:properties}.
